---
title: "EDA_CIA_001"
authors: Nimisha Mary Sam, Nidhi Jaidev, Ujjwal Akshith Mondreti
date: "2025-02-17"
output:
  md_document:
    variant: markdown_github
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Team

We are the Avengers. Our team is made up of the following people:
<br />
<br />
  1. Nimisha Mary Sam - 24221132<br />
  2. Nidhi Jaidev - 24221131<br />
  3. Ujjwal Akshith Mondreti- 24221051<br />

## What we have learnt till CIA 1

  We learnt about the various types of data in R.
  
```{r data_types}
print(typeof("ABC123!@#"))
print(typeof(12345))
print(typeof(12345.67))
```
  Afterwards, we learnt about Vectors and operations on Vectors in R.
  
```{r vectors}
x <- c(1, 2, 3, 4, 5)
y <- c(1, 2, 3, 4, 5)

print(x+y)
print(x*y)
print(x-y)
print(x/y)
```

## Description of the Dataset

  We selected the EuStockMarkets dataset from the built-in datasets library. It contains the daily closing prices of four of the major stock indices in the European Union, i.e., Germany (DAX), Switzerland (SMI), France (CAC) and the UK (FTSE) from 1991 to 1998.

The summary of the dataset is given below:

```{r summary}
summary(EuStockMarkets)
```


## Plotting the Stock Prices

  We plotted all of the stock closing prices per day from 1991 to 1998. We assigned Red to DAX, Blue to SMI, Green to CAC and Purple to FTSE.

```{r plot}
x <- seq_len(nrow(EuStockMarkets))

plot(x, EuStockMarkets[, "DAX"], type="n", main = "Daily Stock Closing Prices", xaxt="n", ylab="Stock Prices", xlab="Years")

colors <- c("red", "blue", "green", "purple")

for (i in seq_len(ncol(EuStockMarkets))) {
  lines(x, EuStockMarkets[,i], col=colors[i])
  years <- as.integer(time(EuStockMarkets))
  tick.posis <- seq(10, length(years), by = 100)
  axis(1, at = tick.posis, las = 2, labels = years[tick.posis])
}
```

## Data Dictionary

The data dictionary of the dataset is given below:

```{r EuStockMarkets_dict}
for (i in 1:10) {
  print(c(EuStockMarkets[i, ]))
}
```

## Business Implications

The dataset used in this report, EuStockMarkets, consists of daily closing prices for four major European stock indices—DAX (Germany), SMI (Switzerland), CAC (France), and FTSE (UK)—from 1991 to 1998. 

1. **Market Trend Analysis:**  
   - The dataset allows businesses and investors to analyze historical trends in European stock markets. This can aid in identifying patterns in stock price movements and economic cycles.

2. **Risk Assessment & Portfolio Management:**  
   - By studying the fluctuations in stock indices, financial analysts can assess risks associated with investments in European markets. This helps in developing diversified portfolios to minimize risk.

3. **Investment Strategies & Forecasting:**  
   - Investors can use past trends to develop predictive models, enabling them to make informed decisions about future investments and hedging strategies.

4. **Macroeconomic Impact:**  
   - The dataset reflects economic events and policies of the time. Businesses can study how macroeconomic changes, such as inflation, interest rate changes, and political events, impacted stock prices.

5. **Market Correlation Studies:**  
   - The dataset enables businesses to analyze correlations between different European markets, which is valuable for multinational corporations and institutional investors managing international portfolios.